Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
boo

The high-resolution data collected by activity-sensing devices, accumulated over a long period such as a patient's lifespan, can result in a substantially greater volume of data than current EHR platforms are designed to handle. To this challenge we present our own personal data platform ``WebBox \cite{webbox}.'' We have used WebBox with EHRs
to enable patient collected data to be augmented with hospital-provided EHR data. WebBox is able to combine
data from multiple sources, and enables patients to make their own annotations against data, and
to optionally share these annotations, along with their activity diaries, with their clinician. This
then enables clinicians and patients to enter into a dialog about how well the patient is doing,
and any lifestyle changes they can make to better their situation.

>>>>

The high-resolution data collected by activity-sensing devices, accumulated over a long period such as a patient's lifespan, can result in a substantially greater volume of data than current EHR platforms are designed to handle. To address this deficiency, we have devised a personal data platform ``WebBox \cite{webbox}'', optimised to handle the secure, long-term storage of structured data at large volume.  Thus far, WebBox has been used to archive clinician (hospital and GP-provided) data, including both raw structured data (such as clinical diagnostic results) and accompanying report documents.  Being optimised for structured data capture and integration, our current work extends this platform to the aforementioned activity profiles, created from retrieving raw sensed data from digital health device APIs and translating such observations to the Activity-SENSE representation.

%Following this, to optionally share these annotations, along with their activity diaries, with their clinician. This then enables clinicians and patients to enter into a dialog about how well the patient is doing, and any lifestyle changes they can make to better their situation.
